---
title: "Association Rules"
author: "Daniel"
date: "7/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Association Rules

*the main aim of the project is performing asscociation analysis using the respective algorithms*

Reading the Data
```{r}
#Installing packages
#install.packages("arules")
library(arules)
```

```{r}
#Loading our data 

Transactions<-read.transactions("http://bit.ly/SupermarketDatasetII", sep = ",")
Transactions
```
Checking the Data 

```{r}
# Verifying the object's class
# ---
# This should show us transactions as the type of data that we will need
# ---
# 
class(Transactions)
```
Previewing our first 5 transactions data results

```{r}
inspect(Transactions[1:5])
```
viewing the items that make up our dataframe,

```{r}
items<-as.data.frame(itemLabels(Transactions))
colnames(items) <- "Item"
head(items, 10)
```
 
solution implementation and modeling

```{r}
# Generating a summary of the transaction dataset
#Informing the marketing department on the most relevant marketing strategies that will result in the highest no. of sales
# 
summary(Transactions)
```
the frequently purchased imtems are as below
 *Mineral Water* 
 *Eggs *
 *Spaghetti* 
 *French Fries* 
 *Chocolate *

 the frequency of some articles 

```{r}
itemFrequency(Transactions[, 5:10],type = "absolute")
round(itemFrequency(Transactions[, 5:10],type = "relative")*100,2)
```

```{r}
par(mfrow = c(1, 2))
# plot the frequency of items
itemFrequencyPlot(Transactions, topN = 10,col="darkgreen")
itemFrequencyPlot(Transactions, support = 0.1,col="darkred")
```
model on association rules we use Min Support as 0.001 and confidence as 0.8

```{r}
rules <- apriori (Transactions, parameter = list(supp = 0.001, conf = 0.8))
rules
```
 
Building a apriori model with Min Support as 0.002 and confidence as 0.8

```{r}
rules2 <- apriori (Transactions,parameter = list(supp = 0.002, conf = 0.8)) 
```

Building apriori model with Min Support as 0.002 and confidence as 0.6

```{r}
rules3 <- apriori (Transactions, parameter = list(supp = 0.001, conf = 0.6)) 
rules2
rules3
```

Observing rules built in our model i.e. first 5 model rules
 

```{r}
inspect(rules[1:5])
# Ordering these rules by a criteria 
# 
rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules[1:5])
```



# Conclusion and Recommendation

the most sold items are
*Mineral Water*
*Eggs*
*Spaghetti*
*French Fries*
*Chocolate*
 


