---
title: "Feature Selection"
author: "Daniel"
date: "7/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Our main Objective is to perfom feature selection to identify the most important features in our dataset

```{r,echo=TRUE}
#loading the first data set to the environment to use in the first session of the project
load_dd<-read.csv("http://bit.ly/CarreFourDataset")
head(load_dd)
```


```{r}
#checking for null values 
colSums(is.na(load_dd))
```

```{r,echo=TRUE}
#checking statistical summary of our dataset
summary(load_dd)
```
from the summary above we can conclude that the data in the gross.margin.percentage is a constant. this is because the min and the max values are the same and the mean are the same





```{r,echo=TRUE}
Sales_df <- load_dd[,c(6,7,8,12,14,15,16)]
head(Sales_df)
```

## Feature Selection

```{r}

# Installing and loading our caret package
# ---
# 
suppressWarnings(
        suppressMessages(if
                         (!require(caret, quietly=TRUE))
                install.packages("caret")))
library(caret)


```

```{r}

# Installing and loading the corrplot package for plotting
# ---
# 
suppressWarnings(
        suppressMessages(if
                         (!require(corrplot, quietly=TRUE))
                install.packages("corrplot")))
library(corrplot)


```

```{r,echo=TRUE}

# Calculating the correlation matrix

correlationMatrix <- cor(Sales_df)

# Find attributes that are highly correlated

highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.6)

# Highly correlated attributes

highlyCorrelated

names(Sales_df[,highlyCorrelated])
```

```{r,echo=TRUE}
# We can remove the variables with a higher correlation 
# and comparing the results graphically as shown below
# ---
# 
# Removing Redundant Features 
# ---
# 
Dataset2<-Sales_df[-highlyCorrelated]

# Performing our graphical comparison 
# ---
# 
par(mfrow = c(1, 2))
corrplot(correlationMatrix, order = "hclust")
corrplot(cor(Dataset2), order = "hclust")

```

from the the correlation plot we could see that there are there re only few columns which can be used in decision making which are
**Ratings**, **unit.price**,**quantity**

